Optimal (Multiway) Spatial Joins

### 2024-05-28 msj.tex
yufei

\noindent {\underline{\em Example 5.2.}} Segment $h_1$ has no left-covering rectangle in $R_2$ and thus has no trimmed segment. Segment $h_2$ has $\beta_2$ and $\beta_3$ as its left-covering rectangles. As the entire $h_2$ is covered by $\beta_2$
\qed

>>>>

\noindent {\underline{\em Example 5.2.}} Segment $h_1$ has no left-covering rectangle in $R_2$ and thus has no trimmed segment. Segment $h_2$ has one left-covering rectangle in $R_2$, which is $\beta_1$. As the entire $h_2$ is covered by $\beta_1$, it is equivalent to its trimmed segment $h_2'$. Segment $h_3$ has two left-covering rectangles in $R_2$, which are $\beta_2$ and $\beta_3$.
\qed
